Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-21 awipev-CO2.Rmd
Went back because previous changes (except the  use of P=0 in pHinsi) were incorrect

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_s_seafet, ALK = at_mean_interp*1e-6, Tinsi = temp_insitu_ctd, Tlab = temp_s_lab, Pinsi = depth/10, S = sal_mix, Pt = 0, Sit = 0))

pH_durafet <- d %>%
#  dplyr::filter(!is.na(pH_s_durafet))
    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
pH_durafet <- pH_durafet %>%
#  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_s_durafet, ALK = at_mean_interp*1e-6, Tinsi = temp_fb, Tlab = temp_s_lab, Pinsi = 0, S = sal_fb, Pt = 0, Sit = 0))

>>>>

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_seafet$pH_s_seafet,ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))

pH_durafet <- d %>%
#  dplyr::filter(!is.na(pH_s_durafet))
    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
pH_durafet <- pH_durafet %>%
#  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= 0, S=pH_durafet$sal_fb, Pt=0, Sit=0))
